Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-07-24 cosmic_voids.tex
Theoretical part of the introduction and references to numerical works on voids

Theoretical 
efforts for describing the evolution of the large-scale universe, leaded 
by the seminal work of \citet{Zeldovich70}, are highly consistent with the 
cosmic web picture, where planar pancake-like regions of matter enclose 
enormous sub-dense voids and are bordered, in turn, by thin filaments and
high-density clumpy knots.

>>>>

On the theoretical side, early descriptions of the evolution of the 
large-scale universe, leaded by the seminal work of \citet{Zeldovich70}, 
are highly consistent with the cosmic web picture, where planar 
pancake-like regions of matter enclose enormous sub-dense voids and are 
bordered, in turn, by thin filaments and high-density clumpy knots. First
theoretical models for describing formation, dynamics and properties of
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
complemented and extended by first numerical studies based on simulations
\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
numerical results from N-body simulations, fuelled by last generation 
computing systems, has become increasingly common in the two last decades
as a powerful analysis tool in studies of cosmic voids \citep{Gottlober03}.
